Programming Future Parallel Architectures\\ with Haskell and Intel ArBB

### 2013-09-30 src2/arbb/paperThesis.tex
apa

\documentclass[conference]{IEEEtran}

\usepackage{graphicx, color, code}
\usepackage[cmex10]{amsmath}
\usepackage{url}
% \usepackage{bookman}  %% bold teletype fonts, but don't know how to prevent it from changing the whole document

@@

\usepackage{courier}
\usepackage{fancyvrb}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\newenvironment{mycode}
{% This is the begin code
  \footnotesize
  \noindent
  \begin{code}\noindent\vspace{-1mm}}
%  \begin{code}\noindent}
{% This is the end code
  \end{code} 
}

@@

\begin{document}
% \title{Painless Portable Vector Parallelism\\ with Haskell and Intel ArBB}
\title{Programming Future Parallel Architectures\\ with Haskell and Intel ArBB}
% \title{Embedded Domain-Specific Languages Pave the Way for New Parallel Architectures}

\author{\IEEEauthorblockN{Bo Joel Svensson}
\IEEEauthorblockA{Dept. of Computer Science and Engineering\\
Chalmers University of Technology\\
Gothenburg, Sweden\\
Email: joels@chalmers.se}
\and
\IEEEauthorblockN{Ryan Newton}
\IEEEauthorblockA{Intel Corporation\\
Hudson, MA\\
Email: rrnewton@gmail.com
}}
% Email: ryan.r.newton@intel.com

\maketitle

\begin{abstract}
%
New parallel architectures, such 
\new{as Cell, Intel MIC, GPUs, and tiled architectures, enable} high
performance but are often hard to program.
What is needed is a bridge between high-level programming models 
where programmers are most productive and modern parallel architectures. 
We propose that that bridge is Embedded Domain Specific Languages (EDSLs).

@@

\end{abstract}
\IEEEpeerreviewmaketitle

% ====================================================================================================
\section{Introduction}
% ====================================================================================================

@@

% ====================================================================================================
\section{Embedded Domain-Specific Languages}
% ====================================================================================================

@@

% ====================================================================================================
% \section{Accelerate and ArBB}
%\section{\accarbb{}:  ArBB and Accelerate}
\section{\accarbb{} $=$ ArBB $+$ Accelerate}
\label{sec:accelerate-arbb}
% ====================================================================================================

@@

%% dotProd :: Vector Float -> 
%%            Vector Float -> 
%%            Acc (Scalar Float) 
\begin{mycode}
dotProd (xs :: Vector Float) 
        (ys :: Vector Float) = 
  \kw{let} xs\_ = use xs 
      ys\_ = use ys 
  \kw{in}  fold (+) 0 (zipWith (*) xs\_ ys\_) 
\end{mycode}

@@

%\subsection{Intel Array Building Blocks (ArBB)}
\section{Intel Array Building Blocks (ArBB)}
\label{sec:arbb}

@@

% ====================================================================================================
\section{Implementation of \systemname{}} 
% ====================================================================================================

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=2.0in]{figure_architecture}    
  \end{center}
\vspace{-5mm}
  \caption{Architecture of the \systemname{} system.  \rn{(ROUGH.)}}
  \label{f:architecture}
\end{figure}

@@

% ====================================================================================================
\section{Preliminary Results}
% ====================================================================================================

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=3.5in]{jit}    
  \end{center}
\vspace{-5mm}
  \caption{Running time experiments including JIT-time.} 
  \label{f:jit}
\end{figure}

\begin{figure}
  \begin{center}
   \includegraphics[width=3.5in]{nojit}    
  \end{center}
\vspace{-5mm}
  \caption{Running time experiments JIT-time excluded.}
  \label{f:nojit}
\end{figure}

@@

% ====================================================================================================
\section{Related Work}
% ====================================================================================================

@@

% ====================================================================================================
\section{Discussion and Conclusions}
% ====================================================================================================

@@

{
\small
% \bibliographystyle{plainnat}
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,haskell_arbb}
}

\end{document}

>>>>

%\documentclass[conference]{IEEEtran}

%\usepackage{graphicx, color, code}
%\usepackage[cmex10]{amsmath}
%\usepackage{url}
% \usepackage{bookman}  %% bold teletype fonts, but don't know how to prevent it from changing the whole document

@@

%\usepackage{courier}
%\usepackage{fancyvrb}

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

@@

\newenvironment{mycode}
{% This is the begin code
  \begin{verbatim}}%
  %\footnotesize
  %\noindent
  %\begin{code}\noindent\vspace{-1mm}}
%  \begin{code}\noindent}
{% This is the end code
  \end{verbatim}
  %\end{code} 
}

@@

%\begin{document}
% \title{Painless Portable Vector Parallelism\\ with Haskell and Intel ArBB}
%\title{Programming Future Parallel Architectures\\ with Haskell and Intel ArBB}
% \title{Embedded Domain-Specific Languages Pave the Way for New Parallel Architectures}

%\author{\IEEEauthorblockN{Bo Joel Svensson}
%\IEEEauthorblockA{Dept. of Computer Science and Engineering\\
%Chalmers University of Technology\\
%Gothenburg, Sweden\\
%Email: joels@chalmers.se}
%\and
%\IEEEauthorblockN{Ryan Newton}
%\IEEEauthorblockA{Intel Corporation\\
%Hudson, MA\\
%Email: rrnewton@gmail.com
%}}
% Email: ryan.r.newton@intel.com

%\maketitle

%\begin{abstract}
%
\subsection*{Abstract}
New parallel architectures, such 
\new{as Cell, Intel MIC, GPUs, and tiled architectures, enable} high
performance but are often hard to program.
What is needed is a bridge between high-level programming models 
where programmers are most productive and modern parallel architectures. 
We propose that that bridge is Embedded Domain Specific Languages (EDSLs).

@@

%\end{abstract}
%\IEEEpeerreviewmaketitle

% ====================================================================================================
\subsection{Introduction}
% ====================================================================================================

@@

% ====================================================================================================
\subsection{Embedded Domain-Specific Languages}
% ====================================================================================================

@@

% ====================================================================================================
% \section{Accelerate and ArBB}
%\section{\accarbb{}:  ArBB and Accelerate}
\subsection{\accarbb{} $=$ ArBB $+$ Accelerate}
\label{sec:accelerate-arbb}
% ====================================================================================================

@@

%% dotProd :: Vector Float -> 
%%            Vector Float -> 
%%            Acc (Scalar Float) 
\begin{verbatim}
dotProd (xs :: Vector Float) 
        (ys :: Vector Float) = 
  \kw{let} xs\_ = use xs 
      ys\_ = use ys 
  \kw{in}  fold (+) 0 (zipWith (*) xs\_ ys\_) 
\end{verbatim}

@@

%\subsection{Intel Array Building Blocks (ArBB)}
\subsection{Intel Array Building Blocks (ArBB)}
\label{sec:arbb}

@@

% ====================================================================================================
\subsection{Implementation of \systemname{}} 
% ====================================================================================================

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=2.0in]{./arbb/figure_architecture}    
  \end{center}
\vspace{-5mm}
  \caption{Architecture of the \systemname{} system.  \rn{(ROUGH.)}}
  \label{f:architecture}
\end{figure}

@@

% ====================================================================================================
\subsection{Preliminary Results}
% ====================================================================================================

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=3.5in]{./arbb/jit}    
  \end{center}
\vspace{-5mm}
  \caption{Running time experiments including JIT-time.} 
  \label{f:jit}
\end{figure}

\begin{figure}
  \begin{center}
   \includegraphics[width=3.5in]{./arbb/nojit}    
  \end{center}
\vspace{-5mm}
  \caption{Running time experiments JIT-time excluded.}
  \label{f:nojit}
\end{figure}

@@

% ====================================================================================================
\subsection{Related Work}
% ====================================================================================================

@@

% ====================================================================================================
\subsection{Discussion and Conclusions}
% ====================================================================================================

@@

%{
%\small
% \bibliographystyle{plainnat}
%\bibliographystyle{IEEEtran}
%\bibliography{IEEEabrv,haskell_arbb}
%}

%\end{document}
